Issues with Dynamical Measurements Across the Disk

### 2019-02-17 paper/ms.tex
Add citation to dynamical center

\section{Discussion} \label{sec:discussion}
We have shown that, in simulation, the ``local midplane'' can have strong
azimuthal dependence. The implications of this finding are not clear, but
clearly demonstrate that assuming our local midplane is the same as the global
midplane is insufficient for extracting the most dynamical information from
the {\em Gaia} mission. We focus our discussion now solely on the midplane.

>>>>

\section{Discussion} \label{sec:discussion}
We have shown that, in simulation, the ``local midplane'' can have strong
azimuthal dependence. The implications of this finding are not clear, but
clearly demonstrate that assuming our local midplane is the same as the global
midplane is insufficient for extracting the most dynamical information from
the {\em Gaia} mission.

While we focus our discussion now solely on the midplane, there is an
additional complication in the measurement of the distance from the Sun to the
Galactic center that may also be important. When modelling stars at Galactic
radii close to the Sun's radius, it is in principle possible to determine what
point they are orbitting about, or in other words the ``dynamic Galactic
center.'' It is not guaranteed that this dynamic Galactic center will coincide
with the distance to Sgr~A\textsuperscript{*} \citep{2018AA...615L..15G}. In
fact, \citet{2015ApJ...803...80K} were able to measure the distance of the Sun
to the Galactic center using dynamical information on Palomar 5, though not to
a precision capable of competing with the distance to
Sgr~A\textsuperscript{*}.
